Borel regularity for ODEs and Thimble Integrals

### 2023-12-07 exp-resurgence.tex
Rephrase Borel regularity for thimbles and new proofs

\begin{brainstorm}
    \item Section~\ref{borel_reg-ODE}---definitely Section~\ref{setting-ODE}, and maybe other subsections--revise the proof of the main result for ODE taking into account the results in our paper
    \item Do flagged revisions in Section~\ref{borel-reg-thimble}
    \item Section~\ref{contour-argument-AL}---revise the general contour argument
    \item Revise Section 2, using the formalism of $\singexp{\sigma}{\Lambda}(\Omega)$
    \begin{itemize}
    \item Replace formalism in Section~\ref{reg-decay}
    \end{itemize}
    \item Check which examples are still in the framework of our theorem
    \begin{itemize}
    \item Start a storage document for shelved examples
    \end{itemize}
    \item Section~\ref{resurgence-AL}---Draw intersection points figure
    \item Section~\ref{sec:mod-bessel-lift}---pin down contour
    \item Explain contour figure in Airy example [explain what the regions indicate and what the color]
    \begin{itemize}
    \item Figure out how to release source code. How much do we need to clean it up? Is it okay that it relies on Shadertoy?
    \end{itemize}
    \item Look at ``Plan of the paper'' appendix and confirm that we've included everything we want
    \begin{itemize}
    \item Put future goals in storage document
    \end{itemize}
    \item Veronica doesn't like $\gamma_z$ as notation for Hankel contour. I'll suggest $\mathcal{H}_{1,z}$ where $1$ is the point where the path is centered. 
\end{brainstorm}

@@

\[ \Phi(z) = \int_{\Lambda} \exp\left[-z \left(4 u^3 - 3 u\right)\right]\,du \]
as
\textcolor{orange}{[How do we know it is a solution of Equation (1)?]}
\color{orange}
\[ e^{z}\, (2\pi)^{-\tfrac{1}{2}}\, \int_{-\infty}^\infty e^{-z t^2/2} \left[ 1 - \frac{2}{3} t + \frac{5}{72} t^2 - \frac{32}{27} t^3 + \frac{385}{31104} t^4 - \frac{224}{81} t^5 + \frac{85085}{33592320} t^6 - \ldots \right] dt \]
using the substitution $\tfrac{1}{2} t^2 = 4 u^3 - 3 u + 1$. Na\"{i}vely integrating term by term, you again get the transmonomial~\eqref{series:bessel-ex}.
\color{black}
Once you have the formal solution $\series{\Phi}$, you might try to get an actual solution by applying {\em Borel summation}, which turns a formal power series into a function asymptotic to it. Borel summation works in three steps.
\begin{enumerate}
\item Thinking of $z$ as a ``frequency variable,'' we take the Borel transform (also known as formal inverse Laplace transform) of $\series{\Phi}$, producing a formal power series $\series{\phi}$ in a new ``position variable'' $\zeta$.
\item If $\series{\phi}$ has a positive radius of convergence we say $\series{\Phi}$ is {\em $1$-Gevrey}. We sum $\series{\phi}$ to get a holomorphic function $\hat{\phi}$ on a neighborhood of $\zeta = 0$. Then, by analytic continuation, we expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$---the continuation of $d\zeta$. %\textcolor{orange}{[Nikita has a complementary picture where the Borel plane is the cotangent fiber? Ask more about this.]}
\item Furthermore, if $\hat{\phi}$ grows slowly enough along an infinite ray $b + e^{i\theta}[0, \infty)$ \textcolor{magenta}{[change, explain, or link to notation]} its Laplace transform $\laplace_b^\theta \hat{\phi}$ (see Section \ref{laplace:ordinary}) turns out to be a holomorphic function of $z$, well-defined on some sector of the frequency plane. In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\hat{\Phi}:=\laplace_b^\theta \hat{\phi}$ its {\em Borel sum} at $b$. 
\end{enumerate}
The series $\series{\Phi}$ and its Borel sum $\hat{\Phi}$ have a special relationship, which is best described in the language of {\em Gevrey asymptoticity}. %\textcolor{magenta}{[Do we need to extend these definitions, and the associated theorems, to cover slight series? Hopefully it wouldn't be too hard, but it would be a pain.]}
\begin{defn}
On an open, possibly bounded sector $\Omega$ around $\infty$, a power series
\begin{equation}\label{series:asymp-defn}
\frac{a_1}{z} + \frac{a_2}{z^2} + \frac{a_3}{z^3} + \frac{a_4}{z^4} + \ldots
\end{equation}
is {\em asymptotic} to a holomorphic function $F$ if
\[ \left|F - \left(\frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_{n-1}}{z^{n-1}} \right) \right| \in o_{z \to \infty}\big(|z|^{-n}\big) \]
over all orders $n$. \textcolor{orange}{Introduce $\sim$ notation.}
\end{defn}
If two power series of the form \eqref{series:asymp-defn} are asymptotic to the same function, they must be equal; this can be deduced from the triangle inequality. The power series which is asymptotic to a given function on a given open sector, if it exists, is therefore an intrinsic property of the function: it's the the function's {\em asymptotic expansion} on that sector. The functions that have asymptotic expansions on a given sector form a ring~\cite[Section~A.4]{nikolaev2023existence}, and the map that sends such a function to its asymptotic expansion is a ring homomorphism.

@@

The central goal of this paper is to explain, from this perspective, why Borel summation works well for the two kinds of problems exemplified in Section~\ref{intro:summation}.
\begin{enumerate}
\item Solving a linear ODE of single level~$1$ \cite[Section 2.1]{EcalleIII}\textcolor{DarkTurquoise}{\cite[Section~5.2.2.1]{diverg-resurg-iii}}. One example is Equation~\eqref{eqn:bessel-rescaled-1}. The general example is the equation $\mathcal{P} \Phi = 0$ given by a differential operator of the form
\[ \mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_{d-1}(z^{-1})\,\partial_z^{d-1} \big], \]
where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial, and $R_0, \ldots, R_{d-1}$ are holomorphic functions in some disk $|z|>A$ around infinity. We'll restrict our attention to the case where the roots of $P$ are simple (see Section \ref{setting-ODE}).

@@

Second of all, we want to explain why it is useful to work in the position domain (the Borel plane): on the one hand integral equations are more regular than differential equations. On the other hand, a thimble integral in the frequency domain can be recast as the Laplace transform of a function in the spatial domain. 
\subsubsection{Why does Borel summation work for solutions of level-$1$ ODEs?}
\textcolor{DarkCyan}{[Let's try to move some technical detail from here to the section where the result is proved. For example:]}

Consider a linear level-$1$ differential operator $\mathcal{P}$ of the form described in~Section~\ref{borel-reg:explanatory-power}. This operator will always have an irregular singularity at $z = \infty$.

@@

However, can we find a distinguished basis for solutions in a purely analytic way? This should be possible because of our regularity assumptions about the coefficients of $\mathcal{P}$. In fact, the Main Asymptotic Existence Theorem (M.A.E.T.) guarantees the existence of an analytic frame of solutions asymptotic to a formal frame (see \cite[Theorem 3.1]{diverg-resurg-iii}), but it is not a constructive method (see \cite[Chapter 14]{balser}). \color{black} \color{Goldenrod}[Let's try to move most of this detail to the proof section.] Conversely, we can explicitly build a distinguished basis of analytic solutions: first going to the position domain, we can consider $d$ integral operators of the form 
\begin{equation}
\hat{P}_j:=P(-\zeta)+\partial_{\zeta,\alpha_j}^{-1}\circ Q(-\zeta)+\partial_{\zeta,\alpha_j}^{-2}\circ\sum_{r=0}^{d-1}R_r(\partial_{\zeta,\alpha_j}^{-1})\circ (-\zeta)^r
\end{equation}
labeled by the roots of $P$. This type of operator is the one we studied in \cite{reg-sing-volterra}, hence we know there exists a unique solution $\psi_j$ of $\hat{P}_j\psi_j=0$, such that $\psi_j$ blows-up as $\zeta_j^{\tau_j-1}$ at $\zeta_j=0$ and it has a controlled behavior on an open domain $\Omega_j$ which is star-shaped at $\alpha_j$ and avoids the other critical points (see the definition in Section \ref{setting-ODE}). In addition, $\psi_j$ can be Laplace transformed, giving a analytic function $\Psi_j:=\laplace_{\zeta_j}^{\theta}\psi_j$. 
At this point, we may ask what is the relationship between the two frames of analytic solutions, namely the Borel sum $\hat{\Psi}_j$ of the formal solutions $\series{\Psi}_j$ and the Laplace transform of $\psi_j$. Our main result says they are actually proportional, hence proving Borel summation works \textcolor{orange}{[add reminder of what it means for Borel summation to ``work'']}.\color{black}
\textcolor{Cyan}{Using the dictionary for the Laplace transform associated with some point $\zeta = \alpha$ in the frequency domain, (link section), we can turn $\mathcal{P}$ into an integral operator $\hat{\mathcal{P}}_\alpha$. If we choose $-\alpha$ to be a root of $P$, then $\hat{\mathcal{P}}_\alpha$ will have a regular singularity at $\zeta = \alpha$, and we understand a lot of details about its specific form~\cite{reg-sing-volterra}. We show in~\cite{reg-sing-volterra} that $\hat{\mathcal{P}}_\alpha \phi = 0$ has a distinguished solution $\psi_\alpha$ which is characterized by having a power-law singularity with a known exponent $\tau_\alpha - 1$ at $\zeta = \alpha$ and having exponentially bounded growth at infinity.}

@@

\subsubsection{Why does Borel summation work for thimble integrals?}
%\textcolor{DarkCyan}{Let $X$ be an $N$-dimensional complex manifold, and $f\colon X\to\C$ a proper holomorphic map with non-degenerate critical points.}
Consider a thimble integral of the form described in Section~\ref{borel-reg:explanatory-power}.
We'll define our setting in the language of translation surfaces, to make clear the connection with our geometric picture of the Laplace transform. The image of $f$ has a natural structure of translation surface---a Riemann surface carrying a holomorphic 1-form $d\zeta$, and $\zeta$ is a translation coordinate. 
For each critical point $a_j$, let $\Gamma_j$ be the ray going rightward from the critical value $\alpha_j$, and let $\zeta_{\alpha_j}$ be the translation coordinate around $\Gamma_j$ which vanishes at $\alpha_j$. These are well-defined as long as $\Gamma_j$ misses the critical values of $f$. Then, the preimage $f^{-1}(\Gamma_j)$ is a bunch of disjoint curves (see Figure \ref{fig:thimble_vs_rays}), as long as $\Gamma_j$ misses the other critical values of $f$. The Lefschetz thimble $\Lambda_j$ can be regarded as the component of $f^{-1}(\Gamma_j)$ that goes through $a_j$.\footnote{\textcolor{orange}{We could orient so that shifting $\Lambda_j$ to its left would make its projection run clockwise around $\Gamma_j$. However, this only seems to be possible when $X$ is 1-dimensional.}}

\begin{figure}[ht]
    \centering
    \includegraphics[scale=0.7]{figures/u_contour_5.pdf}
    \hspace{1cm}
    \includegraphics[scale=0.7]{figures/zeta_contour_5.pdf}
    \caption{\textcolor{orange}{Change the pictures with the one centered at the critical values/points respectively}The preimage of a ray departing from the critical value and going to infinity.}
    \label{fig:thimble_vs_rays}
\end{figure}
Then, our main result for thimble integrals is proving that $1$-dimensional thimble integrals are indeed Borel regular:
\begin{theorem}[see Theorem \ref{thm:maxim-dim}]\label{thm:maxim}
    Let $\tilde{I}_{j}(z)\defeq e^{-z \alpha_j}(2\pi)^{1/2} z^{-1/2} \sum_{n\geq 0}a_{j,n}z^{-n}$ be the asymptotic expansion of $I_j$ as $\Re z e^{i\theta}\to \infty$ for a generic direction $\theta$. Then:
\begin{enumerate}
\item The series $\tilde{\Phi}_j:=z^{1/2} \tilde{I}_j$ is $1$-Gevrey, thus $\tilde{\phi}_j(\zeta)\defeq\borel_\zeta(\tilde{\Phi}_j)$ converges near $\zeta=\alpha_j$
\item If you continue the sum of $\tilde{\phi}_j$ along the ray $ e^{i\theta}[\alpha_j,+\infty)$, and take its Laplace transform along that ray, you'll recover $z^{1/2} I_j$.
\item\label{part3} For any $\zeta$ on the ray going rightward from $\alpha_j$, we have a \textit{thimble projection formula}
\begin{multline}\label{eqn:formula}
\hat{\phi}_{j}(\zeta)=\fracderiv{3/2}{\zeta}{\alpha_j} \left( \int_{\Lambda_j(\zeta)}\nu \right)=\left(\tfrac{\partial}{\partial \zeta}\right)^2\,\frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{\alpha_j}^\zeta (\zeta-\zeta')^{-1/2}\left( \int_{\Lambda_j(\zeta')} \nu \right)\,d\zeta',
\end{multline}
where $\Lambda_j(\zeta)$ is the part of $\Lambda_j$ that goes through $f^{-1}([\alpha_j, \zeta])$. Notice that $\Lambda_j(\zeta)$ starts and ends in $f^{-1}(\zeta)$. \textcolor{magenta}{[The thimble $\Lambda_j$ needs an orientation, but the orientation is arbitrary.]}
\end{enumerate}
\end{theorem}
The idea of the proof is sketched below in the following diagram (for the rigorous one we refer to Section \ref{borel-reg-thimble}).
\[
\begin{tikzcd}
{I}_{j} \arrow[rrr,"\aexp^{\theta}"]\arrow[dd, swap,"\laplace^{-1} "] &  & & \tilde{I}_{j}\arrow[dd,"\borel"]\\
& & &\\
\iota_j \arrow[r,equal] & \hat{\iota}_j & &\tilde{\iota}_{j} \arrow[ll, "\text{sum}"]
\end{tikzcd}
\]
On the one hand, the thimble integral $I_j$ can be regarded as a Laplace type integral, i.e. as the Laplace transform of a function $\iota_j$, written explicitly in equation~\eqref{eqn:formula}. 
On the other hand, we compute the asymptotic expansion of $I_j$ using the saddle point approximation, which turns out to be a formal $1$-Gevrey series in the frequency domain. Consequently, its Borel transform $\series{\iota}_j$ is a germ of holomorphic functions at $\zeta=\alpha_j$ in the position domain. Then, we'll show that the Taylor expansion of $\iota_j$ at $\zeta=\alpha_j$ agrees with $\tilde{\iota}_j$.

The upshot is that thimble integrals are Borel regular because they can be turned into Laplace transforms.
%% the following remark has been moved to Section of the proof
%\begin{remark}\label{rmk:Pham formula}
%    Equation \eqref{eqn:formula} gives an explicit expression for $\phi_j$ in terms of $\nu$ and of the pre-image of the ray $e^{i\theta}[\alpha_j,\zeta)$ via $f$. When $f$ and $\nu$ are polynomials and $X$ is $N$-dimensional, a result of Pham \cite[Equation 2.4, II partie]{pham} allows to write $\hat{\iota}_j$ explicitly as 
%    \begin{equation}\label{eqn:Pham}
 %       (-1)^{\frac{N(N-1)}{2}}  \sum_{k=0}^\infty c_k\, \delta^{-\frac{N}{2}-k}+ \text{ hol. funct.}
 %   \end{equation}
%for some coefficients $c_k$ which depends on $f$ and $\nu$, and with $\delta^{-\alpha}$ be defined as
 %  \begin{equation*}
  %     \delta^{-\alpha}:=\begin{cases}
   %        \frac{\zeta^{\alpha-1}}{-2\pi i(\alpha-1)!}\log(\zeta) + \text{ hol. funct.} & \text{ if } \alpha\in\mathbb{N}^*\\
    %       & \\
     %      \frac{(-\zeta)^{\alpha-1}}{2\pi i \Gamma(-\alpha)}+ \text{ hol. funct.} & \text{ if } \alpha\notin \mathbb{N}^* 
      % \end{cases}
   %\end{equation*}
%In particular, if $N=1$, from equation \eqref{eqn:Pham} we deduce that $\hat{\phi}_j$ is the $1/2-$ derivative of $\hat{\iota}_j$, \textcolor{orange}{hence it has simple singularities \ref{simple-res-thimble}.} We expect this result to hold beyond the polynomial case. We also expect that equation \eqref{eqn:formula} can be generalized to the $N$-dimensional case replacing the $3/2$-derivative with the $(N+1)/2$ one. 
%\end{remark}
%     
\subsubsection{Other results}
%
As part of the treatment, we have made use of some new perspectives on the Laplace transform (see Section~\ref{sec:Laplace-Borel-general}). Indeed, the Laplace transform is often used to solve ODEs on the frequency domain by relating them to ODEs on the position domain. We find, however, that it is much easier and more natural to relate ODEs on the frequency domain to integral equations on the spatial domain. In particular, working with integral equations in the spatial domain will be our main strategy to prove Borel regularity for ODEs (see \cite[Theorem 4]{reg-sing-volterra}).

>>>>

\begin{brainstorm}
    \item Section~\ref{borel_reg-ODE} and maybe other subsections--revise the proof of the main result for ODE taking into account the results in our paper
    \item Do flagged revisions in Section~\ref{borel-reg-thimble}
    \item Section~\ref{contour-argument-AL}---revise the general contour argument
    \item Revise Section 2, using the formalism of $\singexp{\sigma}{\Lambda}(\Omega)$
    \begin{itemize}
    \item Replace formalism in Section~\ref{reg-decay}
    \end{itemize}
    \item Check which examples are still in the framework of our theorem
    \begin{itemize}
    \item Start a storage document for shelved examples
    \end{itemize}
    \item Section~\ref{resurgence-AL}---Draw intersection points figure
    \item Section~\ref{sec:mod-bessel-lift}---pin down contour
    \item Explain contour figure in Airy example [explain what the regions indicate and what the color]
    \begin{itemize}
    \item Figure out how to release source code. How much do we need to clean it up? Is it okay that it relies on Shadertoy?
    \end{itemize}
    \item Look at ``Plan of the paper'' appendix and confirm that we've included everything we want
    \begin{itemize}
    \item Put future goals in storage document
    \end{itemize}
    \item Veronica doesn't like $\gamma_z$ as notation for Hankel contour. I'll suggest $\mathcal{H}_{1,z}$ where $1$ is the point where the path is centered. 
\end{brainstorm}

@@

\[ \Phi(z) = \int_{\Lambda} \exp\left[-z \left(4 u^3 - 3 u\right)\right]\,du \]
as
\textcolor{orange}{[How do we know it is a solution of Equation (1)?]}
\color{orange}
\[ e^{z}\, (2\pi)^{-\tfrac{1}{2}}\, \int_{-\infty}^\infty e^{-z t^2/2} \left[ 1 - \frac{2}{3} t + \frac{5}{72} t^2 - \frac{32}{27} t^3 + \frac{385}{31104} t^4 - \frac{224}{81} t^5 + \frac{85085}{33592320} t^6 - \ldots \right] dt \]
using the substitution $\tfrac{1}{2} t^2 = 4 u^3 - 3 u + 1$. Na\"{i}vely integrating term by term, you again get the transmonomial~\eqref{series:bessel-ex}.
\color{black}
Once you have the formal solution $\series{\Phi}$, you might try to get an actual solution by applying {\em Borel summation}, which turns a formal power series into a function asymptotic to it. Borel summation works in three steps.
\begin{enumerate}
\item Thinking of $z$ as a ``frequency variable,'' we take the Borel transform (also known as formal inverse Laplace transform) of $\series{\Phi}$, producing a formal power series $\series{\phi}$ in a new ``position variable'' $\zeta$.
\item If $\series{\phi}$ has a positive radius of convergence we say $\series{\Phi}$ is {\em $1$-Gevrey}. We sum $\series{\phi}$ to get a holomorphic function $\hat{\phi}$ on a neighborhood of $\zeta = 0$. Then, by analytic continuation, we expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$---the continuation of $d\zeta$. %\textcolor{orange}{[Nikita has a complementary picture where the Borel plane is the cotangent fiber? Ask more about this.]}
\item Furthermore, if $\hat{\phi}$ grows slowly enough along an infinite ray $b + e^{i\theta}[0, \infty)$ \textcolor{magenta}{[change, explain, or link to notation]} its Laplace transform $\laplace_b^\theta \hat{\phi}$ (see Section \ref{laplace:ordinary}) turns out to be a holomorphic function of $z$, well-defined on some sector of the frequency plane. In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\hat{\Phi}:=\laplace_b^\theta \hat{\phi}$ its {\em Borel sum} at $b$. 
\end{enumerate}
The series $\series{\Phi}$ and its Borel sum $\hat{\Phi}$ have a special relationship, which is best described in the language of {\em Gevrey asymptoticity}. %\textcolor{magenta}{[Do we need to extend these definitions, and the associated theorems, to cover slight series? Hopefully it wouldn't be too hard, but it would be a pain.]}
\begin{defn}
On an open, possibly bounded sector $\Omega$ around $\infty$, a power series
\begin{equation}\label{series:asymp-defn}
\frac{a_1}{z} + \frac{a_2}{z^2} + \frac{a_3}{z^3} + \frac{a_4}{z^4} + \ldots
\end{equation}
is {\em asymptotic} to a holomorphic function $F$ if
\[ \left|F - \left(\frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_{n-1}}{z^{n-1}} \right) \right| \in o_{z \to \infty}\big(|z|^{-n}\big) \]
over all orders $n$. We'll use the symbol $\sim$ to denote the asymptotic of $F$, namely we'll write \[F\sim \sum_{n\geq 1} a_n z^{-n}.\]
\end{defn}
If two power series of the form \eqref{series:asymp-defn} are asymptotic to the same function, they must be equal; this can be deduced from the triangle inequality. The power series which is asymptotic to a given function on a given open sector, if it exists, is therefore an intrinsic property of the function: it's the function's {\em asymptotic expansion} on that sector. The functions that have asymptotic expansions on a given sector form a ring~\cite[Section~A.4]{nikolaev2023existence}, and the map that sends such a function to its asymptotic expansion is a ring homomorphism.

@@

The central goal of this paper is to explain, from this perspective, why Borel summation works well for the two kinds of problems exemplified in Section~\ref{intro:summation}.
\begin{enumerate}
\item Solving a linear ODE of single level~$1$ \cite[Section 2.1]{EcalleIII}\textcolor{DarkTurquoise}{\cite[Section~5.2.2.1]{diverg-resurg-iii}}. One example is Equation~\eqref{eqn:bessel-rescaled-1}. The general example is the equation $\mathcal{P} \Phi = 0$ given by a differential operator of the form
\[ \mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_{d-1}(z^{-1})\,\partial_z^{d-1} \big], \]
where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial, and $R_0, \ldots, R_{d-1}$ are holomorphic functions in some disk $|z|>A$ around infinity. We'll restrict our attention to the case where the roots of $P$ are simple (see Section \ref{borel_reg-ODE}).

@@

Second of all, we want to explain why it is useful to work in the position domain (the Borel plane): on the one hand integral equations are more regular than differential equations. On the other hand, a thimble integral in the frequency domain can be recast as the Laplace transform of a function in the spatial domain. 
\subsubsection{Why does Borel summation work for solutions of level $1$ ODEs?}\label{sec:why_borel_ODE}
%\textcolor{DarkCyan}{[Let's try to move some technical detail from here to the section where the result is proved. For example:]}
%
Consider a linear level-$1$ differential operator $\mathcal{P}$ of the form described in~Section~\ref{borel-reg:explanatory-power}. This operator will always have an irregular singularity at $z = \infty$.

@@

However, can we find a distinguished basis for solutions in a purely analytic way? This should be possible because of our regularity assumptions about the coefficients of $\mathcal{P}$. In fact, the Main Asymptotic Existence Theorem (M.A.E.T.) guarantees the existence of an analytic frame of solutions asymptotic to a formal frame (see \cite[Theorem 3.1]{diverg-resurg-iii}), but it is not a constructive method (see \cite[Chapter 14]{balser}). \color{black} \color{Goldenrod}[Let's try to move most of this detail to the proof section.] Conversely, we can explicitly build a distinguished basis of analytic solutions: first going to the position domain, we can consider $d$ integral operators of the form 
\begin{equation}
\hat{P}_j:=P(-\zeta)+\partial_{\zeta,\alpha_j}^{-1}\circ Q(-\zeta)+\partial_{\zeta,\alpha_j}^{-2}\circ\sum_{r=0}^{d-1}R_r(\partial_{\zeta,\alpha_j}^{-1})\circ (-\zeta)^r
\end{equation}
labeled by the roots of $P$. This type of operator is the one we studied in \cite{reg-sing-volterra}, hence we know there exists a unique solution $\psi_j$ of $\hat{P}_j\psi_j=0$, such that $\psi_j$ blows-up as $\zeta_j^{\tau_j-1}$ at $\zeta_j=0$ and it has a controlled behavior on an open domain $\Omega_j$ which is star-shaped at $\alpha_j$ and avoids the other critical points (see the definition in Section \ref{borel_reg-ODE}). In addition, $\psi_j$ can be Laplace transformed, giving a analytic function $\Psi_j:=\laplace_{\zeta_j}^{\theta}\psi_j$. 
At this point, we may ask what is the relationship between the two frames of analytic solutions, namely the Borel sum $\hat{\Psi}_j$ of the formal solutions $\series{\Psi}_j$ and the Laplace transform of $\psi_j$. Our main result says they are actually proportional, hence proving Borel summation works \textcolor{orange}{[add reminder of what it means for Borel summation to ``work'']}.\color{black}
\textcolor{Cyan}{Using the dictionary for the Laplace transform associated with some point $\zeta = \alpha$ in the frequency domain, (link section), we can turn $\mathcal{P}$ into an integral operator $\hat{\mathcal{P}}_\alpha$. If we choose $-\alpha$ to be a root of $P$, then $\hat{\mathcal{P}}_\alpha$ will have a regular singularity at $\zeta = \alpha$, and we understand a lot of details about its specific form~\cite{reg-sing-volterra}. We show in~\cite{reg-sing-volterra} that $\hat{\mathcal{P}}_\alpha \phi = 0$ has a distinguished solution $\psi_\alpha$ which is characterized by having a power-law singularity with a known exponent $\tau_\alpha - 1$ at $\zeta = \alpha$ and having exponentially bounded growth at infinity.}

@@

\subsubsection{Why does Borel summation work for thimble integrals?}
%\textcolor{DarkCyan}{Let $X$ be an $N$-dimensional complex manifold, and $f\colon X\to\C$ a proper holomorphic map with non-degenerate critical points.}
Consider a thimble integral of the form described in Section~\ref{borel-reg:explanatory-power}. We'll define our setting in the language of translation surfaces, to make clear the connection with our geometric picture of the Laplace transform. The codomain of $f$ has a natural structure of translation surface---a Riemann surface carrying a holomorphic 1-form $d\zeta$, and $\zeta$ is a translation coordinate. \textcolor{RoyalBlue}{[The important thing about $\C$, where $f$ takes values, is htat it's a translation surface---\ldots]} For each critical point $a_j$, let $\Gamma_j$ be the ray going rightward from the critical value $\alpha_j$, and let $\zeta_{\alpha_j}$ be the translation coordinate around $\Gamma_j$ which vanishes at $\alpha_j$. These are well-defined as long as $\Gamma_j$ misses the critical values of $f$. Then, the preimage $f^{-1}(\Gamma_j)$ is a bunch of disjoint curves (see Figure \ref{fig:thimble_vs_rays}), as long as $\Gamma_j$ misses the other critical values of $f$. The Lefschetz thimble $\Lambda_j$ can be regarded as the component of $f^{-1}(\Gamma_j)$ that goes through $a_j$.\textcolor{orange}{We could orient so that shifting $\Lambda_j$ to its left would make its projection run clockwise around $\Gamma_j$. However, this only seems to be possible when $X$ is 1-dimensional.}

\begin{figure}[ht]
    \centering
    \includegraphics[scale=0.7]{figures/u_contour_5.pdf}
    \hspace{1cm}
    \includegraphics[scale=0.7]{figures/zeta_contour_5.pdf}
    \caption{\textcolor{orange}{Change the pictures with the one centered at the critical values/points respectively}The preimage of a ray departing from the critical value and going to infinity.}
    \label{fig:thimble_vs_rays}
\end{figure}

Let $I_j$ be the thimble integral through the thimble $\Lambda_j$ 
\begin{equation}
I_j(z)\defeq\int_{\Lambda_j}e^{-zf}\nu
our main results give an explicit description of $I_j$ as a Laplace transform, and show that $I_j$ is indeed Borel regular. In fact, thimble integrals are Borel regular because they can be turned into Laplace transforms.
\begin{theorem}[see Theorem \ref{thm:thimble_proj_formula-proof}]\label{thm:thimble_proj_formula}
The intgral $I_j$ is the Laplace transform $\laplace_{\alpha_j}^\theta \iota_j$ of the function $\iota_j$ given by the {\em thimble projection formula}
\begin{align}\label{eqn:formula}
\iota_{j} & = \partial_\zeta \left( \int_{\Lambda_j(\zeta)}\nu \right)
\end{align}
where $\Lambda_j(\zeta)$ is the part of $\Lambda_j$ that goes through $f^{-1}([\alpha_j,\zeta])$. Notice that $\Lambda_j(\zeta)$ starts and ends in $f^{-1}(\zeta)$. \textcolor{magenta}{[The thimble $\Lambda_j$ needs an orientation, but the orientation is arbitrary.]}
\end{theorem}
%\begin{remark}
%The operator $\fracderiv{1/2}{\zeta}{\alpha}$ is the fractional derivative based at $\zeta = \alpha$, as defined in Section~\ref{L-int-op}:
%\partial^{1/2}_{\zeta, \alpha} & \defeq \tfrac{\partial}{\partial \zeta} \, \partial^{3/2}_{\zeta, %\alpha} \\[2mm]
%[\partial^{3/2}_{\zeta, \alpha} g](p) & \defeq \frac{1}{\Gamma(\tfrac{1}{2})} \int_{\zeta = \alpha}^p \big(\zeta(p)-\zeta\big)^{-1/2} g\,d\zeta.
%\begin{verify}
%[\partial^{0+1/2}_{\zeta, \alpha} f](p) & = \left(\tfrac{\partial}{\partial \zeta}\right)^{0+1} \partial^{1/2-1}_{\zeta, \alpha} \\
%& = \left(\tfrac{\partial}{\partial \zeta(p)}\right)^{0+1} \frac{1}{\Gamma(1-1/2)} \int_{\zeta = \alpha}^p \big(\zeta(p)-\zeta\big)^{-1/2} f\,d\zeta
%\end{verify}
%\end{remark}
\begin{theorem}[see Theorem \ref{thm:maxim-proof}]\label{thm:maxim}
The function $I_j$ is Borel regular. More explicitly: \textcolor{orange}{[Try to keep on one line]}
\begin{enumerate}
\item As $z \to \infty$ along the ray $z \in e^{i\theta}\,\R_{>0}$, the function $I_j$ is asymptotic to a trans-monomial $\tilde{I}_{j}(z)\in e^{-z \alpha_j} z^{-1/2} \C\llbracket z^{-1}\rrbracket$.
\item The series $\tilde{\Phi}_j:=z^{1/2} \tilde{I}_j$ is $1$-Gevrey. In other words, $\tilde{\phi}_j \defeq \borel_\zeta \tilde{\Phi}_j$ converges near $\zeta=\alpha_j$.
\item If you continue the sum of $\tilde{\phi}_j$ along the ray \textcolor{magenta}{$\Gamma_j^\theta$}, and take its Laplace transform along that ray, you'll recover $z^{1/2} I_j$.
\end{enumerate}
\end{theorem}
\color{Goldenrod}
Then, our main result for thimble integrals is proving they are indeed Borel regular:
\begin{theorem}[see Theorem \ref{thm:maxim-dim}]
    Let $\tilde{I}_{j}(z)\in e^{-z \alpha_j} z^{-1/2} \C\llbracket z^{-1}\rrbracket$ be the asymptotic expansion of $I_j$ as $\Re z e^{i\theta}\to \infty$ for the generic direction $\theta$. Then:
\begin{enumerate}
\item The series $\tilde{\Phi}_j:=z^{1/2} \tilde{I}_j$ is $1$-Gevrey, thus $\tilde{\phi}_j(\zeta)\defeq\borel_\zeta(\tilde{\Phi}_j)$ converges near $\zeta=\alpha_j$
\item If you continue the sum of $\tilde{\phi}_j$ along the ray $ e^{i\theta}[\alpha_j,+\infty)$, and take its Laplace transform along that ray, you'll recover $z^{1/2} I_j$.
\item\label{part3} For any $\zeta$ on the ray going rightward from $\alpha_j$, we have a \textit{thimble projection formula}
\begin{multline}
\hat{\phi}_{j}(\zeta)=\fracderiv{3/2}{\zeta}{\alpha_j} \left( \int_{\Lambda_j(\zeta)}\nu \right)=\left(\tfrac{\partial}{\partial \zeta}\right)^2\,\frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{\alpha_j}^\zeta (\zeta-\zeta')^{-1/2}\left( \int_{\Lambda_j(\zeta')} \nu \right)\,d\zeta',
\end{multline}
where $\Lambda_j(\zeta)$ is the part of $\Lambda_j$ that goes through $f^{-1}([\alpha_j, \zeta])$. Notice that $\Lambda_j(\zeta)$ starts and ends in $f^{-1}(\zeta)$. \textcolor{magenta}{[The thimble $\Lambda_j$ needs an orientation, but the orientation is arbitrary.]}
\end{enumerate}
\end{theorem}
We sketch the proofs of the main results in the following diagram (for the rigorous ones see Section~\ref{borel-reg-thimble}):
\[
\begin{tikzcd}
{I}_{j} \arrow[rrr,"\aexp^{\theta}"]\arrow[dd, swap,"\laplace^{-1} "] &  & & \tilde{I}_{j}\arrow[dd,"\borel"]\\
& & &\\
\iota_j \arrow[r,equal] & \hat{\iota}_j & &\tilde{\iota}_{j} \arrow[ll, "\text{sum}"]
\end{tikzcd}
\]
On the one hand, with a change of coordinates, the thimble integral $I_j$ can be written as a Laplace type integral, i.e. as the Laplace transform of a function $\iota_j$, written explicitly in equation~\eqref{eqn:formula}. 
On the other hand, we compute the asymptotic expansion of $I_j$ using the saddle point approximation, which turns out to be a formal $1$-Gevrey series in the frequency domain. Consequently, its Borel transform $\series{\iota}_j$ is a germ of holomorphic functions at $\zeta=\alpha_j$ in the position domain. Then, we'll show that the Taylor expansion of $\iota_j$ at $\zeta=\alpha_j$ agrees with $\tilde{\iota}_j$.
